---
title: "Exploring the data - Jade"
author: "Jade Sweeney"
date: "01/04/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(tsibble)
library(ggfortify)
library(grid)
library(gridExtra)
```

```{r}
gaa$Team_Outcome <- as.factor(gaa$Team_Outcome)

# For question, other teams' performance in Croke Park
dublin <- gaa %>% filter(Opp_Name == "DUBLIN" | Team_Name == "DUBLIN") %>% 
  filter(Venue == "CROKE PARK")
# 31 observations

mayo <- gaa %>% filter(Opp_Name == "MAYO" | Team_Name == "MAYO") %>% 
  filter(Venue == "CROKE PARK") %>%  filter(Division == "1")
# 12 observations
 
kerry <- gaa %>% filter(Opp_Name == "KERRY" | Team_Name == "KERRY") %>% 
  filter(Venue == "CROKE PARK") %>%  filter(Division == "1")
# 8 observations

cork <- gaa %>% filter(Opp_Name == "CORK" | Team_Name == "CORK") %>% 
  filter(Venue == "CROKE PARK") %>%  filter(Division == "1")
# 10 observations

# If we want to look at Dublin's performance in other venues, not much to choose from
dub <-  gaa %>% filter(Opp_Name == "DUBLIN" | Team_Name == "DUBLIN")
 
dub_parnell <- gaa %>% filter(Opp_Name == "DUBLIN" | Team_Name == "DUBLIN") %>% filter(Venue == "PARNELL PARK")
# 11 observations

dub_mchale <- gaa %>% filter(Opp_Name == "DUBLIN" | Team_Name == "DUBLIN") %>% filter(Venue == "MCHALE PARK")
# 3 observations

dub_fitz <- gaa %>% filter(Opp_Name == "DUBLIN" | Team_Name == "DUBLIN") %>% filter(Venue == "FITZGERALD STADIUM")
# 4 observations


```
 We do not have enough data to do Dublin's performance elsewhere in my opinion.


Let's say I want to now create a variable that gives the number of wins.
For Croke Park. We want to focus on performance, so whether they win or lose, and how many points they score.
```{r}
# Creates a new variable Winner that tells us whether the team in question won or not

mayo1 <- mayo %>%
  mutate(Winner = case_when(Team_Name == "MAYO" & Team_Outcome == "WIN" ~ 'MAYO',
                            Team_Name == "MAYO" & Team_Outcome == "LOSS" ~ 'OTHER TEAM',
                            Opp_Name == "MAYO" & Team_Outcome == "LOSS" ~ 'MAYO',
                            Opp_Name == "MAYO" & Team_Outcome == "WIN" ~ 'OTHER TEAM'))

kerry1 <- kerry %>%
  mutate(Winner = case_when(Team_Name == "KERRY" & Team_Outcome == "WIN" ~ 'KERRY',
                            Team_Name == "KERRY" & Team_Outcome == "LOSS" ~ 'OTHER TEAM',
                            Opp_Name == "KERRY" & Team_Outcome == "LOSS" ~ 'KERRY',
                            Opp_Name == "KERRY" & Team_Outcome == "WIN" ~ 'OTHER TEAM'))

dublin1 <- dublin %>%
  mutate(Winner = case_when(Team_Name == "DUBLIN" & Team_Outcome == "WIN" ~ 'DUBLIN',
                            Team_Name == "DUBLIN" & Team_Outcome == "LOSS" ~ 'OTHER TEAM',
                            Opp_Name == "DUBLIN" & Team_Outcome == "LOSS" ~ 'DUBLIN',
                            Opp_Name == "DUBLIN" & Team_Outcome == "WIN" ~ 'OTHER TEAM'))

cork1 <-cork %>%
  mutate(Winner = case_when(Team_Name == "CORK" & Team_Outcome == "WIN" ~ 'CORK',
                            Team_Name == "CORK" & Team_Outcome == "LOSS" ~ 'OTHER TEAM',
                            Opp_Name == "CORK" & Team_Outcome == "LOSS" ~ 'CORK',
                            Opp_Name == "CORK" & Team_Outcome == "WIN" ~ 'OTHER TEAM'))




new <- rbind(cork1,dublin1,kerry1,mayo1)

new %>% ggplot(aes(Winner, fill = Winner)) + geom_bar() +facet_wrap(Winner)
```

```{r}

dublin2 <- dublin %>%
  mutate(Winner = case_when(Team_Name == "DUBLIN" & Team_Score<Opp_Score ~ 'DUBLIN',
                            Team_Name == "DUBLIN" & Team_Score>Opp_Score  ~ 'OTHER TEAM',
                            Opp_Name == "DUBLIN" & Team_Score<Opp_Score  ~ 'DUBLIN',
                            Opp_Name == "DUBLIN" & Team_Score>Opp_Score  ~ 'OTHER TEAM',
                            Opp_Name == "DUBLIN" & Team_Score==Opp_Score  ~ 'TIE',
                            Team_Name == "DUBLIN" & Team_Score==Opp_Score  ~ 'TIE'))

cork2 <- cork %>%
  mutate(Winner = case_when(Team_Name == "CORK" & Team_Score<Opp_Score ~ 'CORK',
                            Team_Name == "CORK" & Team_Score>Opp_Score  ~ 'OTHER TEAM',
                            Opp_Name == "CORK" & Team_Score<Opp_Score  ~ 'CORK',
                            Opp_Name == "CORK" & Team_Score>Opp_Score  ~ 'OTHER TEAM',
                            Opp_Name == "CORK" & Team_Score==Opp_Score  ~ 'TIE',
                            Team_Name == "CORK" & Team_Score==Opp_Score  ~ 'TIE'))

kerry2 <- kerry %>%
  mutate(Winner = case_when(Team_Name == "KERRY" & Team_Score<Opp_Score ~ 'KERRY',
                            Team_Name == "KERRY" & Team_Score>Opp_Score  ~ 'OTHER TEAM',
                            Opp_Name == "KERRY" & Team_Score<Opp_Score  ~ 'KERRY',
                            Opp_Name == "KERRY" & Team_Score>Opp_Score  ~ 'OTHER TEAM',
                            Opp_Name == "KERRY" & Team_Score==Opp_Score  ~ 'TIE',
                            Team_Name == "KERRY" & Team_Score==Opp_Score  ~ 'TIE'))

mayo2 <- mayo %>%
  mutate(Winner = case_when(Team_Name == "MAYO" & Team_Score<Opp_Score ~ 'MAYO',
                            Team_Name == "MAYO" & Team_Score>Opp_Score  ~ 'OTHER TEAM',
                            Opp_Name == "MAYO" & Team_Score<Opp_Score  ~ 'MAYO',
                            Opp_Name == "MAYO" & Team_Score>Opp_Score  ~ 'OTHER TEAM',
                            Opp_Name == "MAYO" & Team_Score==Opp_Score  ~ 'TIE',
                            Team_Name == "MAYO" & Team_Score==Opp_Score  ~ 'TIE'))

new1 <- rbind(dublin2,cork2,kerry2,mayo2)

new1 %>% ggplot(aes(Winner, fill = Winner)) + geom_bar()

```

Plot that highlights the number of wins and losses for each of the 4 teams in Croke Park. It clearly shows that Dublin has a much higher number of wins compared to the others, but also that is has played many more times in Croke Park.
```{r}
dub_plot <- dublin2 %>% ggplot(aes(Winner, fill = Winner)) + geom_bar(show.legend = FALSE) + ylim(0,25)
mayo_plot <- mayo2 %>% ggplot(aes(Winner, fill = Winner)) + geom_bar(show.legend = FALSE) + ylim(0,25)
kerry_plot <- kerry2 %>% ggplot(aes(Winner, fill = Winner)) + geom_bar(show.legend = FALSE) + ylim(0,25)
cork_plot <- cork2 %>% ggplot(aes(Winner, fill = Winner)) + geom_bar(show.legend = FALSE) + ylim(0,25)

grid.arrange(dub_plot,mayo_plot,kerry_plot,cork_plot, ncol=2, nrow=2,
     top = textGrob("Number of Wins in Croke Park",gp=gpar(fontsize=20,font=3)))
```

