---
title: "ST302 Project"
author: "Mikaela Sminia, Con McCord and Jade Sweeney"
date: "29/04/22"
output:
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(tsibble)
library(ggfortify)
library(grid)
library(gridExtra)
library(xlsx)
library(readxl)
library(ggalt)
library(plotly)
```

## An Analysis of the Performance of the Dublin Gaelic Football Team from 2001 – 2017 {.tabset}

### Introduction
The data set used to conduct this analysis is the “GAA” data set comprising of data related to 1994 National Football League (NFL) games which occurred from 2001 to 2017. The NFL is an annual Gaelic football competition which is contested by the senior county teams. The teams are divided into four divisions with team ability decreasing with the division numbers. The teams initially play each other once receiving league points for each win. Towards the end of the competition the top ranked teams play each other in the knockout stages to determine the overall winner. 

Each game was described in the data using 13 variables initially. These variables contained data describing the teams playing (Team_Name and Opp_Name), the date of the game (Date), the round of the competition (Game_Round), the outcome for the team named in the Team_Name variable (Team_Outcome, the goals, points and total score of each team (Team_Points, Team_Goals, Team_Score, Opp_Points, Opp_Goals and Opp_Score), the venue the match took place in (Venue) and which division the match took place in (Division). 

Our question of interest is “does Croke Park have an impact on the Dublin Gaelic football team’s performance”. This is a topic of interest in contemporary Irish sport arising in part due to the dominance of the Dublin team in recent years. Croke Park is a stadium and headquarters of the Gaelic Athletic Association (GAA) and is where the most important games are held. It is situated in Dublin and thus the Dublin team and as their fans do not have to travel to another county for many of their games in contrast to every other county team. Many pundits argue that this gives Dublin a home advantage in these games although Parnell Park (another stadium in Dublin) is Dublin’s actual home stadium while Croke Park is considered de jure to be a neutral ground. 

To answer this question the data was adjusted to make it suitable for analysis, the findings of said analysis will be presented in various visualisations and a conclusion will then be drawn based on these. 

### Data adjustments
```{r, message = FALSE}
load("gaa.Rdata")

# These are the teams have played the highest number of matches in Croke Park.

# Filter by all Divisiion 1 Dublin matches. Then create a new Winner column which uses the Scores to identify the winnner of the match. This shows whether our team in question won the match, the other team won or if it was a tie.
dub_gaa <- gaa %>% filter(Opp_Name == "DUBLIN" | Team_Name == "DUBLIN") %>% filter(Division == "1")%>%
  mutate(Winner = case_when(Team_Name == "DUBLIN" & Team_Score<Opp_Score ~ 'DUBLIN',
                            Team_Name == "DUBLIN" & Team_Score>Opp_Score  ~ 'OTHER TEAM',
                            Opp_Name == "DUBLIN" & Team_Score<Opp_Score  ~ 'DUBLIN',
                            Opp_Name == "DUBLIN" & Team_Score>Opp_Score  ~ 'OTHER TEAM',
                            Opp_Name == "DUBLIN" & Team_Score==Opp_Score  ~ 'TIE',
                            Team_Name == "DUBLIN" & Team_Score==Opp_Score  ~ 'TIE'))

# Filter by all Divisiion 1 Cork matches. Then create a new Winner column which uses the Scores to identify the winnner of the match. This shows whether our team in question won the match, the other team won or if it was a tie.
cork_gaa <- gaa %>% filter(Opp_Name == "CORK" | Team_Name == "CORK") %>%  filter(Division == "1")%>%
  mutate(Winner = case_when(Team_Name == "CORK" & Team_Score<Opp_Score ~ 'CORK',
                            Team_Name == "CORK" & Team_Score>Opp_Score  ~ 'OTHER TEAM',
                            Opp_Name == "CORK" & Team_Score<Opp_Score  ~ 'CORK',
                            Opp_Name == "CORK" & Team_Score>Opp_Score  ~ 'OTHER TEAM',
                            Opp_Name == "CORK" & Team_Score==Opp_Score  ~ 'TIE',
                            Team_Name == "CORK" & Team_Score==Opp_Score  ~ 'TIE'))

# Filter by all Divisiion 1 Mayo matches. Then create a new Winner column which uses the Scores to identify the winnner of the match. This shows whether our team in question won the match, the other team won or if it was a tie.
mayo_gaa <- gaa %>% filter(Opp_Name == "MAYO" | Team_Name == "MAYO") %>%  filter(Division == "1")%>%
  mutate(Winner = case_when(Team_Name == "MAYO" & Team_Score<Opp_Score ~ 'MAYO',
                            Team_Name == "MAYO" & Team_Score>Opp_Score  ~ 'OTHER TEAM',
                            Opp_Name == "MAYO" & Team_Score<Opp_Score  ~ 'MAYO',
                            Opp_Name == "MAYO" & Team_Score>Opp_Score  ~ 'OTHER TEAM',
                            Opp_Name == "MAYO" & Team_Score==Opp_Score  ~ 'TIE',
                            Team_Name == "MAYO" & Team_Score==Opp_Score  ~ 'TIE'))

# Filter by all Divisiion 1 Kerry matches. Then create a new Winner column which uses the Scores to identify the winnner of the match. This shows whether our team in question won the match, the other team won or if it was a tie.
kerry_gaa <- gaa %>% filter(Opp_Name == "KERRY" | Team_Name == "KERRY") %>%  filter(Division == "1")%>%
  mutate(Winner = case_when(Team_Name == "KERRY" & Team_Score<Opp_Score ~ 'KERRY',
                            Team_Name == "KERRY" & Team_Score>Opp_Score  ~ 'OTHER TEAM',
                            Opp_Name == "KERRY" & Team_Score<Opp_Score  ~ 'KERRY',
                            Opp_Name == "KERRY" & Team_Score>Opp_Score  ~ 'OTHER TEAM',
                            Opp_Name == "KERRY" & Team_Score==Opp_Score  ~ 'TIE',
                            Team_Name == "KERRY" & Team_Score==Opp_Score  ~ 'TIE'))

# There are multiple empty Venue variables so I export these datasets as excel files.
write.xlsx(dub_gaa, file = "dub_gaa.xlsx",
           sheetName = "GAA", append = FALSE)
write.xlsx(kerry_gaa, file = "kerry_gaa.xlsx",
           sheetName = "GAA", append = FALSE)
write.xlsx(cork_gaa, file = "cork_gaa.xlsx",
           sheetName = "GAA", append = FALSE)
write.xlsx(mayo_gaa, file = "mayo_gaa.xlsx",
           sheetName = "GAA", append = FALSE)
```

```{r, message = FALSE}

# Adding in the new variables

# In Excel I added the missing information in the dataset and saved as new excel file. Then uploaded into R again.
load("gaa.Rdata")
cork_gaa <- read_excel("cork_gaa.xlsx")
dub_gaa <- read_excel("dub_gaa.xlsx")
kerry_gaa <- read_excel("kerry_gaa.xlsx")
mayo_gaa <- read_excel("mayo_gaa.xlsx")


# Filter the datasets by Croke Park
dublin <- dub_gaa %>% filter(Venue == "CROKE PARK")
cork <- cork_gaa %>% filter(Venue == "CROKE PARK")
mayo <- mayo_gaa %>%  filter(Venue == "CROKE PARK") 
kerry <- kerry_gaa %>% filter(Venue == "CROKE PARK") 

# Bind these together into a new dataset
new <- rbind(dublin,cork,kerry,mayo)
```

### Analysis
  

```{r, echo = FALSE,fig.dim = c(10, 6)}
# Load in the gaa excel files ( which have the added venue variables)

dublin <- dub_gaa %>% filter(Venue == "CROKE PARK") %>%
  mutate(Winner = case_when(Team_Name == "DUBLIN" & Team_Score<Opp_Score ~ 'DUBLIN',
                            Team_Name == "DUBLIN" & Team_Score>Opp_Score  ~ 'OTHER TEAM',
                            Opp_Name == "DUBLIN" & Team_Score<Opp_Score  ~ 'DUBLIN',
                            Opp_Name == "DUBLIN" & Team_Score>Opp_Score  ~ 'OTHER TEAM',
                            Opp_Name == "DUBLIN" & Team_Score==Opp_Score  ~ 'TIE',
                            Team_Name == "DUBLIN" & Team_Score==Opp_Score  ~ 'TIE'))

cork <- cork_gaa %>% filter(Venue == "CROKE PARK") %>%
  mutate(Winner = case_when(Team_Name == "CORK" & Team_Score<Opp_Score ~ 'CORK',
                            Team_Name == "CORK" & Team_Score>Opp_Score  ~ 'OTHER TEAM',
                            Opp_Name == "CORK" & Team_Score<Opp_Score  ~ 'CORK',
                            Opp_Name == "CORK" & Team_Score>Opp_Score  ~ 'OTHER TEAM',
                            Opp_Name == "CORK" & Team_Score==Opp_Score  ~ 'TIE',
                            Team_Name == "CORK" & Team_Score==Opp_Score  ~ 'TIE'))

mayo <- mayo_gaa %>%  filter(Venue == "CROKE PARK")  %>%
  mutate(Winner = case_when(Team_Name == "MAYO" & Team_Score<Opp_Score ~ 'MAYO',
                            Team_Name == "MAYO" & Team_Score>Opp_Score  ~ 'OTHER TEAM',
                            Opp_Name == "MAYO" & Team_Score<Opp_Score  ~ 'MAYO',
                            Opp_Name == "MAYO" & Team_Score>Opp_Score  ~ 'OTHER TEAM',
                            Opp_Name == "MAYO" & Team_Score==Opp_Score  ~ 'TIE',
                            Team_Name == "MAYO" & Team_Score==Opp_Score  ~ 'TIE'))

 
kerry <- kerry_gaa %>% filter(Venue == "CROKE PARK") %>%
  mutate(Winner = case_when(Team_Name == "KERRY" & Team_Score<Opp_Score ~ 'KERRY',
                            Team_Name == "KERRY" & Team_Score>Opp_Score  ~ 'OTHER TEAM',
                            Opp_Name == "KERRY" & Team_Score<Opp_Score  ~ 'KERRY',
                            Opp_Name == "KERRY" & Team_Score>Opp_Score  ~ 'OTHER TEAM',
                            Opp_Name == "KERRY" & Team_Score==Opp_Score  ~ 'TIE',
                            Team_Name == "KERRY" & Team_Score==Opp_Score  ~ 'TIE'))

new <- rbind(dublin,cork,kerry,mayo)

```

  
This next plot shows the top 4 teams and their performance at Croke Park. We can clearly see that Dublin plays in Croke Park at a much higher frequency, does this give them an advantage in and of itself? We can also clearly see that Dublin's win to loss ratio is much much higher than the other 4 teams.   

```{r, echo = FALSE,fig.dim = c(10, 6)}

dub_plot <- dublin %>% ggplot(aes(Winner, fill = Winner)) + geom_bar(show.legend = FALSE, colour = "gray40") + ylim(0,30)  + labs(subtitle = "Dublin", x = NULL, y = "Number of Wins") + scale_fill_manual(values=c("#88b8fd","dark blue","808080")) 

mayo_plot <- mayo %>% ggplot(aes(Winner, fill = Winner)) + geom_bar(show.legend = FALSE, colour = "gray40") + ylim(0,30)  + labs(subtitle = "Mayo", x = NULL, y = "Number of Wins") + scale_fill_manual(values=c("#ff0000","green4","808080"))

kerry_plot <- kerry %>% ggplot(aes(Winner, fill = Winner)) + geom_bar(show.legend = FALSE, colour = "gray40") + ylim(0,30)  + labs(subtitle = "Kerry", x = NULL, y = "Number of Wins") + scale_fill_manual(values=c("#ffff00","chartreuse4","808080"))

cork_plot <- cork %>% ggplot(aes(Winner, fill = Winner)) + geom_bar(show.legend = FALSE, colour = "gray40") + ylim(0,30)  + labs(subtitle = "Cork", x = NULL, y = "Number of Wins") + scale_fill_manual(values=c("#ff0000","white","808080"))

grid.arrange(dub_plot,mayo_plot,kerry_plot,cork_plot, ncol=2, nrow=2,
     top = textGrob("Top 4 Teams' Performance in Croke Park",gp=gpar(fontsize=15,font=4)))
```
  
  
This next plot shows Dublin's performance in its most played stadiums. Again we see that Dublin has played in Croke Park very frequently and again its win to loss ratio is much higher in Croke Park than in other stadiums.  

```{r,echo = FALSE,fig.dim = c(10, 6)}
dub_croke <- dub_gaa %>% filter(Venue == "CROKE PARK") %>%
  mutate(Winner = case_when(Team_Name == "DUBLIN" & Team_Score<Opp_Score ~ 'DUBLIN',
                            Team_Name == "DUBLIN" & Team_Score>Opp_Score  ~ 'OTHER TEAM',
                            Opp_Name == "DUBLIN" & Team_Score<Opp_Score  ~ 'DUBLIN',
                            Opp_Name == "DUBLIN" & Team_Score>Opp_Score  ~ 'OTHER TEAM',
                            Opp_Name == "DUBLIN" & Team_Score==Opp_Score  ~ 'TIE',
                            Team_Name == "DUBLIN" & Team_Score==Opp_Score  ~ 'TIE'))

dub_parnell <- dub_gaa %>% filter(Venue == "PARNELL PARK") %>%
  mutate(Winner = case_when(Team_Name == "DUBLIN" & Team_Score<Opp_Score ~ 'DUBLIN',
                            Team_Name == "DUBLIN" & Team_Score>Opp_Score  ~ 'OTHER TEAM',
                            Opp_Name == "DUBLIN" & Team_Score<Opp_Score  ~ 'DUBLIN',
                            Opp_Name == "DUBLIN" & Team_Score>Opp_Score  ~ 'OTHER TEAM',
                            Opp_Name == "DUBLIN" & Team_Score==Opp_Score  ~ 'TIE',
                            Team_Name == "DUBLIN" & Team_Score==Opp_Score  ~ 'TIE'))

dub_mchale <- dub_gaa %>% filter(Venue == "MCHALE PARK") %>%
  mutate(Winner = case_when(Team_Name == "DUBLIN" & Team_Score<Opp_Score ~ 'DUBLIN',
                            Team_Name == "DUBLIN" & Team_Score>Opp_Score  ~ 'OTHER TEAM',
                            Opp_Name == "DUBLIN" & Team_Score<Opp_Score  ~ 'DUBLIN',
                            Opp_Name == "DUBLIN" & Team_Score>Opp_Score  ~ 'OTHER TEAM',
                            Opp_Name == "DUBLIN" & Team_Score==Opp_Score  ~ 'TIE',
                            Team_Name == "DUBLIN" & Team_Score==Opp_Score  ~ 'TIE'))

dub_fitz <- dub_gaa %>% filter(Venue == "FITZGERALD STADIUM") %>%
  mutate(Winner = case_when(Team_Name == "DUBLIN" & Team_Score<Opp_Score ~ 'DUBLIN',
                            Team_Name == "DUBLIN" & Team_Score>Opp_Score  ~ 'OTHER TEAM',
                            Opp_Name == "DUBLIN" & Team_Score<Opp_Score  ~ 'DUBLIN',
                            Opp_Name == "DUBLIN" & Team_Score>Opp_Score  ~ 'OTHER TEAM',
                            Opp_Name == "DUBLIN" & Team_Score==Opp_Score  ~ 'TIE',
                            Team_Name == "DUBLIN" & Team_Score==Opp_Score  ~ 'TIE'))

dubnew <- rbind(dub_croke,dub_fitz,dub_mchale,dub_parnell)

```

These next plots repeat the same information, except this time in pie chart form. This shows the porportion of wins instead of the number. It shows that Dublin is the 2nd most wins with this, with Cork having a higher percentage of wins in Croke Park.  The next plot strongly highlights that Dublin has the highest percentage of wins in Croke Park than in any other stadium.

```{r, echo = FALSE,fig.dim = c(10, 6)}

fitz_pie <- ggplot(data = dub_fitz, aes(x=1,fill=Winner)) + geom_bar(position="fill", colour = "gray40") +
  coord_polar(theta="y")  + labs(subtitle = "Fitzgerald Stadium", x = NULL, y = NULL) + scale_fill_manual(values=c("#88b8fd","dark blue","808080")) + theme_void()

croke_pie <- ggplot(data = dub_croke, aes(x=1,fill=Winner)) + geom_bar(position="fill", colour = "gray40") +
  coord_polar(theta="y")  + labs(subtitle = "Croke Park", x = NULL, y = NULL) + scale_fill_manual(values=c("#88b8fd","dark blue","808080"))+ theme_void()

parnell_pie <- ggplot(data = dub_parnell, aes(x=1,fill=Winner)) + geom_bar(position="fill", colour = "gray40") +
  coord_polar(theta="y")   + labs(subtitle = "Parnell Park", x = NULL, y = NULL) + scale_fill_manual(values=c("#88b8fd","dark blue","808080"))+ theme_void()

mchale_pie <- ggplot(data = dub_mchale, aes(x=1,fill=Winner),) + geom_bar(position="fill", colour = "gray40")+ coord_polar(theta="y")   + labs(subtitle = "McHale Park", x = NULL, y = NULL) + scale_fill_manual(values=c("#88b8fd","dark blue","808080")) + theme_void()

grid.arrange(croke_pie,parnell_pie,mchale_pie,fitz_pie, ncol=2, nrow=2,
     top = textGrob("Dublin's Wins Across Top 4 Stadiums",gp=gpar(fontsize=15,font=4)))

```

This interactive plot highlights the winning team scores across all their matches they won in Croke Park, and Dublin's scores in their top played venues. It shows that Dublin actually has scored the highest pointwise in their games in Croke Park, both against the other teams who have played in Croke Park and against the other venues they have played. This again shows that Dublin does play better in Croke Park than in other venues.

```{r, echo = FALSE,fig.dim = c(10, 6)}
# Creates titles for the subplot
a <- list(text = "Winning Points Scored by Dublin in Top Venues",xref = "paper",yref = "paper",
  yanchor = "bottom",xanchor = "center", align = "center", x = 0.5,y = 1,showarrow = FALSE)

b <- list(text = "Points Scored by Winners in Croke Park",xref = "paper", yref = "paper",
  yanchor = "bottom",xanchor = "center",align = "center",x = 0.5, y = 1,showarrow = FALSE)

# Remove variables that are not needed
new1 <- new %>% 
  subset (select = -c(Team_Outcome, Date, Game_Round,Team_Goals,Opp_Goals,Team_Points, Opp_Points, Division))

# A new dataset of the Croke Park variable, that gives the Winner Score
gaa_croke <- new1 %>% 
  mutate(Winner_Score = case_when(
                            Opp_Name == "DUBLIN" & Team_Score<Opp_Score  ~ Opp_Score,
                            Opp_Name == "DUBLIN" & Team_Score>Opp_Score  ~ Team_Score,
                            
                            Opp_Name == "CORK" & Team_Score<Opp_Score  ~ Opp_Score,
                            Opp_Name == "CORK" & Team_Score>Opp_Score  ~ Team_Score,
                            
                            Opp_Name == "KERRY" & Team_Score<Opp_Score  ~ Opp_Score,
                            Opp_Name == "KERRY" & Team_Score>Opp_Score  ~ Team_Score,
                            
                            Opp_Name == "MAYO" & Team_Score<Opp_Score  ~ Opp_Score,
                            Opp_Name == "MAYO" & Team_Score>Opp_Score  ~ Team_Score))

# Remove variables where there is a tie, where there are NA's and include only the relevant winning teams.
gaa_croke[is.na(gaa_croke)] = 0
gaa_croke <- gaa_croke[gaa_croke$Winner_Score !=0,]
gaa_croke <- gaa_croke %>% filter(Winner != "OTHER TEAM")

# Create a plot that shows the score of each of the winning teams and make it interactive.
plot <- ggplot(gaa_croke, aes(x= Winner_Score, y = Winner, color = Winner, shape= Winner)) + 
  geom_jitter(width = 0.5, size = 2.5) + 
  labs(y = NULL, x = "Score") + 
  scale_colour_brewer(palette = "Dark2") + ##changed it to dark to make a better contrast
  scale_shape_manual(values = c("DUBLIN" = 16, "CORK" = 15, "KERRY" =17, "MAYO" =18 )) + ##add shape 
  theme(legend.position="none")
croke_plot <- ggplotly(plot, tooltip = c("x","y")) %>%
  layout(annotations = b)



#########
# Same steps as previous but using Dublin games in its top 4 venues
dubnew1 <- dubnew %>% 
  subset (select = -c(Team_Outcome, Date, Game_Round,Team_Goals,Opp_Goals,Team_Points, Opp_Points,Division))

gaa_dublin <- dubnew1 %>% 
  mutate(Dublin_Score = case_when(
                            Opp_Name == "DUBLIN" & Team_Score<Opp_Score  ~ Opp_Score,
                            Opp_Name == "DUBLIN" & Team_Score>Opp_Score  ~ Team_Score)) #Changed Winner_Score to Dublin_Score For thr dublin plot

gaa_dublin[is.na(gaa_dublin)] = 0
gaa_dublin <- gaa_dublin[gaa_dublin$Dublin_Score !=0,]
gaa_dublin <- gaa_dublin %>% filter(Winner != "OTHER TEAM")


plot2 <- ggplot(gaa_dublin, aes(x= Dublin_Score, y = Venue, color = Venue)) + 
  geom_jitter(width = 0.5, size = 2.5) + 
  labs(y = NULL, x = "Score") + 
  scale_colour_brewer(palette = "Accent") + ##changed colour cause too close to the team plot colours
  theme(legend.position="none")  
dub_plot <- ggplotly(plot2, tooltip = c("x","y")) %>%
  layout(annotations = a) ###Removed the colour variable cause it is a repeat

# Combine both plots together
subplot(dub_plot, croke_plot, nrows=1, margin = 0.05, titleX = TRUE, titleY = TRUE)
```
### Conclusion
a concluding paragraph summarising your finds.

### Responsibilities
I, Con Anthony Mc Cord had primary responsibility for the material in XXXXX. 

I, Jade Eve Sweeney had primary responsibility for the material in XXXXX. 

I, Mikaela Jaya Sminia had primary responsibility for the material in XXXXX. 

 

Although each team member had a section for which they were primarily responsible the input of each team member was invaluable for each one of us in completing our individual sections. This report required the skills of each team member in its completion.  

