---
title: "Code"
author: "Mikaela Sminia 19250793"
date: "3/29/2022"
output: html_document
---
librarys
```{r}
library("tidyverse")
load("gaa.Rdata")
```


```{r}

g <- gaa %>% 
  filter(Venue == "CROKE PARK")
g
dublin_gaa<- gaa %>% 
  filter(Venue == "CROKE PARK") %>% 
  filter(Opp_Name == "DUBLIN"| Opp_Name == "DUBLIN")
dublin_gaa
#31
gaa %>% 
  filter(Venue == "CROKE PARK") %>% 
  filter(Team_Name == "KERRY"|Opp_Name == "KERRY")
#8
gaa %>% 
  filter(Venue == "CROKE PARK") %>% 
  filter(Team_Name == "TYRONE" |Opp_Name =="TYRONE" )
#9
gaa %>% 
  filter(Venue == "CROKE PARK") %>% 
  filter(Team_Name == "MAYO" |Opp_Name =="MAYO" )
#12
gaa %>% 
  filter(Venue == "CROKE PARK") %>% 
  filter(Team_Name == "DONEGAL" |Opp_Name =="DONEGAL" )
#10
```

Graphs
### First graph(basic)
1. bar graph showing the way dublin has played in all stadiums(x)
2. CROKE PARk highlighted green
3. according to wins/points scored?
```{r}
dublin_gaa<- gaa %>% 
  filter(Opp_Name == "DUBLIN") %>% 
  filter(Team_Outcome == "LOSS") %>%   #dublin is always Opp
  count(Venue)
  ggplot(aes(x= Venue , y=Team_Outcome))+
  geom_histogram()
dublin_gaa


```

### Second graph
1. bar graph showing the way all teams has played in CROKE PARK
2. DUBLIN highlighted in dublin color
3. according to wins/points scored?

### Third Graph (3d)
1. venue vs teams vs wins
2. where do each team win the most
3. Dublin, CROKE PARK highlighted in green
4. Everyone else in orange
5. star every outlier
