---
title: "Code"
author: "Mikaela Sminia 19250793"
date: "3/29/2022"
output: html_document
---
librarys
```{r}
library("tidyverse")
load("gaa.Rdata")
library(scatterplot3d)
library(plotly)
```

# gaa data

## code to check for na's in columns 
```{r}
#NOT for seeing where they are
sum(is.na(gaa$Venue)|gaa$Venue == "")
sum(is.na(gaa$Team_Outcome)|gaa$Team_Outcome == "UNKNOWN")
#Venue is the only one with missing values
```

### Code for all teams we are looking at with all venues
```{r}
DUBLIN_gaa<- gaa %>%
  filter(Team_Name == "DUBLIN"| Opp_Name == "DUBLIN")

KERRY_gaa <- gaa %>% 
  filter(Team_Name == "KERRY"|Opp_Name == "KERRY")

CORK_gaa <- gaa %>%  
  filter(Team_Name == "CORK" |Opp_Name =="CORK" )

MAYO_gaa<- gaa %>%
  filter(Team_Name == "MAYO" |Opp_Name =="MAYO" )

county_gaa1 <- rbind(DUBLIN_gaa,KERRY_gaa,CORK_gaa,MAYO_gaa) %>% 
  subset (select = -c(Team_Outcome, Date, Game_Round,Team_Goals,Opp_Goals,Team_Points, Opp_Points))#removes these things as do not plan to use them
  
county_gaa1 #with all extra teams

```

## improved with Winner variable found in JAdes code
Dublin
Cork
Kerry
Mayo
```{r}
  
county_gaa2 <- county_gaa1 %>%
  mutate(Winner = case_when(Team_Name == "DUBLIN" & Team_Score<Opp_Score ~ 'DUBLIN',
                            Team_Name == "DUBLIN" & Team_Score>Opp_Score  ~ 'OTHER TEAM',
                            Opp_Name == "DUBLIN" & Team_Score<Opp_Score  ~ 'DUBLIN',
                            Opp_Name == "DUBLIN" & Team_Score>Opp_Score  ~ 'OTHER TEAM',
                            Opp_Name == "DUBLIN" & Team_Score==Opp_Score  ~ 'TIE',
                            Team_Name == "DUBLIN" & Team_Score==Opp_Score  ~ 'TIE',
                            Team_Name == "CORK" & Team_Score<Opp_Score ~ 'CORK',
                            Team_Name == "CORK" & Team_Score>Opp_Score  ~ 'OTHER TEAM',
                            Opp_Name == "CORK" & Team_Score<Opp_Score  ~ 'CORK',
                            Opp_Name == "CORK" & Team_Score>Opp_Score  ~ 'OTHER TEAM',
                            Opp_Name == "CORK" & Team_Score==Opp_Score  ~ 'TIE',
                            Team_Name == "CORK" & Team_Score==Opp_Score  ~ 'TIE',
                            Team_Name == "KERRY" & Team_Score<Opp_Score ~ 'KERRY',
                            Team_Name == "KERRY" & Team_Score>Opp_Score  ~ 'OTHER TEAM',
                            Opp_Name == "KERRY" & Team_Score<Opp_Score  ~ 'KERRY',
                            Opp_Name == "KERRY" & Team_Score>Opp_Score  ~ 'OTHER TEAM',
                            Opp_Name == "KERRY" & Team_Score==Opp_Score  ~ 'TIE',
                            Team_Name == "KERRY" & Team_Score==Opp_Score  ~ 'TIE',
                            Team_Name == "MAYO" & Team_Score<Opp_Score ~ 'MAYO',
                            Team_Name == "MAYO" & Team_Score>Opp_Score  ~ 'OTHER TEAM',
                            Opp_Name == "MAYO" & Team_Score<Opp_Score  ~ 'MAYO',
                            Opp_Name == "MAYO" & Team_Score>Opp_Score  ~ 'OTHER TEAM',
                            Opp_Name == "MAYO" & Team_Score==Opp_Score  ~ 'TIE',
                            Team_Name == "MAYO" & Team_Score==Opp_Score  ~ 'TIE'))
county_gaa2
```
# Venues filter
Venue == "CROKE PARK"
Venue == "PARNELL PARK"
Venue == "MCHALE PARK"
Venue == "FITZGERALD STADIUM"
Base on Jades code
```{r}
venue_gaa1 <- county_gaa2 %>% 
  filter(Venue == c("CROKE PARK", "PARNELL PARK", "MCHALE PARK", "FITZGERALD STADIUM"))
```
### Creat a colume called Winner_score. Tie= Na
```{r}

venue_gaa2 <- venue_gaa1 %>% 
  mutate(Winner_Score = case_when(
                            Opp_Name == "DUBLIN" & Team_Score<Opp_Score  ~ Opp_Score,
                            Opp_Name == "DUBLIN" & Team_Score>Opp_Score  ~ Team_Score,
                            
                            Opp_Name == "CORK" & Team_Score<Opp_Score  ~ Opp_Score,
                            Opp_Name == "CORK" & Team_Score>Opp_Score  ~ Team_Score,
                            
                            Opp_Name == "KERRY" & Team_Score<Opp_Score  ~ Opp_Score,
                            Opp_Name == "KERRY" & Team_Score>Opp_Score  ~ Team_Score,
                            
                            Opp_Name == "MAYO" & Team_Score<Opp_Score  ~ Opp_Score,
                            Opp_Name == "MAYO" & Team_Score>Opp_Score  ~ Team_Score))

venue_gaa2[is.na(venue_gaa2)] = 0 #Lets na which are ties be 0

venue_gaa2
```


### Option two no filter for venue 
```{r}
county_gaa3 <- county_gaa2%>% 
  mutate(Winner_Score = case_when(
                            Opp_Name == "DUBLIN" & Team_Score<Opp_Score  ~ Opp_Score,
                            Opp_Name == "DUBLIN" & Team_Score>Opp_Score  ~ Team_Score,
                            
                            Opp_Name == "CORK" & Team_Score<Opp_Score  ~ Opp_Score,
                            Opp_Name == "CORK" & Team_Score>Opp_Score  ~ Team_Score,
                            
                            Opp_Name == "KERRY" & Team_Score<Opp_Score  ~ Opp_Score,
                            Opp_Name == "KERRY" & Team_Score>Opp_Score  ~ Team_Score,
                            
                            Opp_Name == "MAYO" & Team_Score<Opp_Score  ~ Opp_Score,
                            Opp_Name == "MAYO" & Team_Score>Opp_Score  ~ Team_Score))

county_gaa3[is.na(county_gaa3)] = 0 #Lets na which are ties be 0
county_gaa3
```
# Remove the "OTHER TEAM and TIE" variables with all venues
```{r}
g <- subset(county_gaa3, Winner != "OTHER TEAM")
county_gaa4 <-subset(g, Winner != "TIE")
county_gaa4
```
#Fill in the venue with UNKNOWN variable 
-Other and Tie removed
```{r}
county_gaa4$Venue[county_gaa4$Venue==''] <- "UNKNOWN"
```

